GO

### 2020-03-25 analysis/12_GO.Rmd
new GO anlysis, new candidate gnee list

```{r}
candidates <- c("PRL", "PRLR", 
                 "AVP", "VIP", "AVPR1A", "AVPR1B", "OXT",  "VIPR1", "VIPR2",
                "GNRH1", "NPY", "LH", "FSH",
                "CRH", "FSHB", "GH",  "JAK2", "HCRT", "TRH", "TSHB",
                "MC3R", "MC4R", "MC5R",  "NR3C1", "NR3C2",
                "ESR1", "ESR2", "AR", 
                "STAT5B", "CISH",
                "GNRHR", "NPVF")

@@

DEG_path <- "../results/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "03_DEGs.*") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)

DEGs <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>%
  mutate(comparison = sapply(strsplit(as.character(file_name),'../results/03_DEGs.'), "[", 2)) %>% 
  mutate(comparison = sapply(strsplit(as.character(comparison),'.csv'), "[", 1)) %>% 
  select(gene, comparison)
head(DEGs)
```

@@

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior",
                   "candidategenes")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
```

@@

```{r}
candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control.bldg"), contains("bldg.lay"), contains("lay.inc.d3"),
         contains("inc.d3.inc.d9"), contains("inc.d9.inc.d17"), contains("inc.d17.hatch"),
         contains("hatch.n5"), contains("n5.n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)
row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
candidate_DEGs <- tail(candidate_DEGs,10)
kable(candidate_DEGs)

# Top Go terms: reponse to keytone, response to hormone, repsponse to organonitrogen compound, positive regulation of homeostatic process, maternal beahvior

>>>>

```{r}
candidates <- c("OXT", "AVP", "GNRH1", "GNRHR", 
                    "AR", "POMC", "AGRP", 
                       "CRH", "AVPR1A", "AVPR1B", "AVPR2","VIP",
                       "CYP19A1", "DRD1", "DRD2", "PRL", "PRLR", "SOX9", 
                    "ESR1","ESR2", "LBH", "CDK1", "BRCA1",
                    "PTEN", "CREBBP", "FOS", "JUN", "EGR1",
                     "BDNF", "GRM2","GRIA1",
                    "KCNJ5", "CISH", "PTGER3", "CEBPD", "ZBTB16", 
                    "DIO3", "DIO2", "DIO1",

                     "VIPR1", "VIPR2", "NPY", "LH", "FSH", "FSHB",
                    "JAK2", "HCRT", "TRH", "TSHB",
                    "MC3R", "MC4R", "MC5R",  "NR3C1", "NR3C2",
                    "STAT5B","NPVF")

@@

DEG_path <- "../results/DEseq2/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs.csv") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)

DEGs <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>%
  mutate(comparison = sapply(strsplit(as.character(file_name),'../results/DEseq2/*'), "[", 2)) %>% 
  mutate(comparison = sapply(strsplit(as.character(comparison),'_DEGs.csv'), "[", 1)) %>% 
  select(gene, comparison)
head(DEGs)
```

@@

```{r GO_DEGs}
GO_DEGs <- left_join(allGO, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>% 
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control_bldg"), contains("bldg_lay"), contains("lay_inc.d3"),
         contains("inc.d3_inc.d9"), contains("inc.d9_inc.d17"), contains("inc.d17_hatch"),
         contains("hatch_n5"), contains("n5_n9")) %>%
  filter(GO %in% c("endocrineprocess", "lactation", 
                   "parentalbehavior", "matingbehavior",
                   "candidategenes")) %>% 
  map(~.x) %>%
  discard(~all(is.na(.x))) %>%
  map_df(~.x)
```

@@

```{r}
candidate_DEGs <- left_join(candidates, DEGs) %>%
  arrange(GO, gene) %>%
  group_by(GO, comparison) %>%
  summarize(genes = str_c(gene, collapse = ", ")) %>%
  pivot_wider(names_from = comparison, values_from = genes) %>% 
  select(GO, contains("control_bldg"), contains("bldg_lay"), contains("lay_inc.d3"),
         contains("inc.d3_inc.d9"), contains("inc.d9_inc.d17"), contains("inc.d17_hatch"),
         contains("hatch_n5"), contains("n5_n9"))
candidate_DEGs <- as.data.frame(candidate_DEGs)

row.names(candidate_DEGs) <- candidate_DEGs$GO  
candidate_DEGs <- t(candidate_DEGs)
candidate_DEGs <- as.data.frame(candidate_DEGs)
kable(candidate_DEGs)

bioprocshinyGO <- c("topBiologicalProcessGO",
                    "Prostate gland growth",
                    "Cellular response to hormone stimulus",
                    "Response to endogenous stimulus",
                    "Mammary gland development",
                    "Response to hormone",
                    "Response to endogenous stimulus",
                    NA,
                    "Regulation of animal organ morphogenesis",
                    "Temperature homeostasis",
                    "Prostate gland growth",
                    NA,NA,NA,
                    "Cellular response to hormone stimulus",
                    NA,
                    "Regulation of cell communication",
                    NA,
                    "Cell-cell signaling",
                    "Cellular response to hormone stimulus",
                    "Positive regulation of ossification",
                    "G2 DNA damage checkpoint"
                    )

candidate_DEGs <- cbind(candidate_DEGs, bioprocshinyGO)
kable(candidate_DEGs)
